---
title: 'calheatmapR'
---

```{r echo=FALSE}
library(calheatmapR)
```

Initialises a calendar heatmap that uses all default values.

### Usage

```{r eval=FALSE}
calheatmapR(data = pletcher)
```

### Arguments

argument | details | cal-heatmap equivalent
---------|---------|-----------------------
data | list, each element is a number, with a timestamp for a name | [dataFormat](http://kamisama.github.io/cal-heatmap/#data-format)
width | element width |
height | element height |

### Examples

Passing an empty list to `calheatmapR` will create a default cal-heatmap. (As you can see the height argument need work, as it creates an element that is far larger than necessary.)

```{r}
calheatmapR(data = list())
```

If we add data to the function, such as the example data included in the package, called `pletcher` (see [data](data.html)), we still get the default plot, we need to customise the plot using customisation functions [`chDomain`](chDomain.html), [`chLabel`](chLabel.html) and [`chLegend`](chLegend.html)

```{r}
data(pletcher)
calheatmapR(data = pletcher, width = "100%", height = "100%")
```
