---
title: 'chDomain'
---
```{r echo=FALSE}
library(calheatmapR)
```

Allows customisation of the domain elements in a calendar heatmap.

### Usage

```{r eval=FALSE}
calheatmapR(data = demoData) %>%
    chDomain(domain = "hour", subDomain = "min", range = 10)
```

### Arguments

argument | details | cal-heatmap equivalent
---------|------|---------|---------|--------
calheatmapR | a calendar heatmap returned by `calheatmapR` |
domain | type of domain | [domain](https://kamisama.github.io/cal-heatmap/#domain)
subDomain | type of subDomain | [subDomain](https://kamisama.github.io/cal-heatmap/#subDomain)
start | Date, in format YYYY-MM-DD | [start](https://kamisama.github.io/cal-heatmap/#start)
range | number of domains to display | [range](https://kamisama.github.io/cal-heatmap/#range)
cellSize | size of each domain (in pixels) | [cellSize](https://kamisama.github.io/cal-heatmap/#cellSize)
cellPadding | space between each subDomain (pixels) | [cellPadding](https://kamisama.github.io/cal-heatmap/#cellPadding)
cellRadius | border radius of subDomain cells, for round corners (pixels) | [cellRadius](https://kamisama.github.io/cal-heatmap/#cellRadius)
gutter | space between each domain | [domainGutter](https://kamisama.github.io/cal-heatmap/#domainGutter)
margin | margins around each domain | [domainMargin](https://kamisama.github.io/cal-heatmap/#domainMargin)
colLimit | number of columns to split domains into | [colLimit](https://kamisama.github.io/cal-heatmap/#colLimit)
rowLimit | number of rows to split domains into | [rowLimit](https://kamisama.github.io/cal-heatmap/#rowLimit)
dynamicDimension | dynamic width and height of domains | [domainDynamicDimension](https://kamisama.github.io/cal-heatmap/#domainDynamicDimension)
verticalOrientation | display calendar heatmap vertically | [verticalOrientation](https://kamisama.github.io/cal-heatmap/#verticalOrientation)

### Examples

For this example we'll use the example data set included in the package which tracks the performance of a jockey across 3 months, it charts the percentage of horses he beat in each of the races he rode in.

```{r}

```
