---
title: 'chLabel'
---
```{r echo=FALSE}
library(calheatmapR)
```

Allows customisation of the Label elements, including item names, in a calendar heatmap.

### Usage

```{r eval=FALSE}
calheatmapR(data = pletcher) %>%
    chLabel(position = "top", itemName = "items")
```

### Arguments

argument | details | cal-heatmap equivalent
---------|---------|-----------------------
calheatmapR | a calendar heatmap returned by `calheatmapR` |
position | position of the label, with respect to the domain | [label.position](http://kamisama.github.io/cal-heatmap/#label)
align | alignment of the label, with respect to the domain | [label.align](http://kamisama.github.io/cal-heatmap/#label)
rotate | rotation for vertical label, default is NULL, but accepts "left" or "right" | [label.rotate](http://kamisama.github.io/cal-heatmap/#label)
width | applied when label is rotated, defines width of label | [label.width](http://kamisama.github.io/cal-heatmap/#label)
offset | additional control for label positioning | [label.offset](http://kamisama.github.io/cal-heatmap/#label)
height | height of the domain label (in pixels) | [label.height](http://kamisama.github.io/cal-heatmap/#label)
itemName | name of entity on calendar being presented | [itemName](http://kamisama.github.io/cal-heatmap/#itemName)

### Examples

The `pletcher` data set is used again, along with the [`chDomain`](chDomain.html) function to customise the domain.  First a look at a calendar heatmap without any Label customisation:

```{r}
data(pletcher)

calheatmapR(data = pletcher, height = "100%") %>%
    chDomain(domain = "month",
             subDomain = "day",
             start = "2012-11-01",
             range = 5)
```

Now to customise the label, and itemNames (used in tooltip when hovering over a subDomain).

```{r}
calheatmapR(data = pletcher, height = "100%") %>%
    chDomain(domain = "month",
             subDomain = "day",
             start = "2012-11-01",
             range = 5) %>%
    chLabel(position = "right",
            rotate = "right",
            align = "left",
            width = 20,
            itemName = "% horses beaten")
```

Combining the code found in the example of [`chLegend`](chLegend.html) we can achieve a smart plot

```{r}
calheatmapR(data = pletcher, height = "100%") %>%
    chDomain(domain = "month",
             subDomain = "day",
             start = "2012-11-01",
             range = 5) %>%
    chLegend(legend = seq(10, 90, 10),
             colours = list(min = "#D8D8D8",
                            max = "#D9220F",
                            empty = "#424242"),
             cellSize = 15,
             cellPadding = 5) %>%
    chLabel(position = "right",
            rotate = "right",
            align = "left",
            width = 20,
            itemName = "% horses beaten")
```

<a href="https://github.com/durtal/calheatmapR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
