---
title: 'chLabel'
---
```{r echo=FALSE}
library(calheatmapR)
```

Allows customisation of the Label elements, including item names, in a calendar heatmap.

### Usage

```{r eval=FALSE}
calheatmapR(data = pletcher) %>%
    chLabel(position = "top", itemName = "items")
```

### Arguments

argument | details | cal-heatmap equivalent
---------|---------|-----------------------
calheatmapR | a calendar heatmap returned by `calheatmapR` |
position | position of the label, with respect to the domain | [label.position](http://kamisama.github.io/cal-heatmap/#label)
align | alignment of the label, with respect to the domain | [label.align](http://kamisama.github.io/cal-heatmap/#label)
rotate | rotation for vertical label, default is NULL, but accepts "left" or "right" | [label.rotate](http://kamisama.github.io/cal-heatmap/#label)
width | applied when label is rotated, defines width of label | [label.width](http://kamisama.github.io/cal-heatmap/#label)
offset | additional control for label positioning | [label.offset](http://kamisama.github.io/cal-heatmap/#label)
height | height of the domain label (in pixels) | [label.height](http://kamisama.github.io/cal-heatmap/#label)
itemName | name of entity on calendar being presented | [itemName](http://kamisama.github.io/cal-heatmap/#itemName)

### Examples

The `pletcher` data set is used again, along with the [`chDomain`](chDomain.html) function to customise the domain.  First a look at a calendar heatmap without any Label customisation:

```{r}
data(pletcher)

calheatmapR(data = pletcher, height = "100%") %>%
    chDomain(domain = "month",
             subDomain = "day",
             start = "2012-11-01",
             range = 5)
```

Now to customise the label, and itemNames (used in tooltip when hovering over a subDomain).

```{r}
calheatmapR(data = pletcher, height = "100%") %>%
    chDomain(domain = "month",
             subDomain = "day",
             start = "2012-11-01",
             range = 5) %>%
    chLabel(position = "right",
            rotate = "right",
            align = "left",
            width = 20,
            itemName = "% horses beaten")
```

Combining the code found in the example of [`chLegend`](chLegend.html) we can achieve a smart plot

```{r}
calheatmapR(data = pletcher, height = "100%") %>%
    chDomain(domain = "month",
             subDomain = "day",
             start = "2012-11-01",
             range = 5) %>%
    chLegend(legend = seq(10, 90, 10),
             colours = list(min = "#D8D8D8",
                            max = "#D9220F",
                            empty = "#424242"),
             cellSize = 15,
             cellPadding = 5) %>%
    chLabel(position = "right",
            rotate = "right",
            align = "left",
            width = 20,
            itemName = "% horses beaten")
```
