---
title: 'data'
---

```{r echo=FALSE}
library(calheatmapR)
```

The **pletcher** dataset is an example of the required format for the [`calheatmapR`](calheatmapR.html) function.

```{r}
data(pletcher)
head(pletcher, 3)
```

The names of the object are timestamps (in seconds), eg `r names(pletcher)[1]` which is `r as.POSIXct(as.numeric(names(pletcher)[1]), origin = "1970-01-01")`.  To create timestamps in R, convert `POSIXct` class into numeric:

```{r}
(timestamp <- as.POSIXct("2000-01-01") %>% as.numeric())
```

To convert a timestamp back to a Date (`POSIXct`) (if using names from a list, as seen in the `pletcher` dataset, they will first need converting from character into numeric.

```{r}
timestamp %>% as.POSIXct(origin = "1970-01-01")
```

So the first value in the `pletcher` dataset is. (Going a step further and converting the Date into a character, this can then be used as the parameter for the `start` argument in the [`chDomain`](chDomain.html) function).

```{r}
names(pletcher)[1] %>% as.numeric %>% as.POSIXct(origin = "1970-01-01")
```

<a href="https://github.com/durtal/calheatmapR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
